Thoughts on resubmission within ARC1

### 2009-03-16 doc/client/client_technical.tex
Updated for the internal release of D2.2-1

The \texttt{Migrate} method behave in much the same way as the \texttt{Submit}
method, but is conceptually different from that method. The \texttt{Migrate}
method takes two additional arguments. A {\URL} \texttt{url} which is
the jobid of a job which should be migrated, and a boolean
\texttt{forcemigration} which will indicate if the job, specified in the
{\JobDescription} \texttt{jobdesc}, should persist if the cluster
({\ExecutionTarget}) does not succeed submitting a kill/terminate request
for the job specified by \texttt{url}. The \texttt{Migrate} method will
also fill the {\XMLNode} \texttt{info} variable with information about the
job for later job management, which additionally include the old jobid
(\texttt{url}) of the migrated job.

@@

The \texttt{Migrate} method:
\begin{shaded}
\begin{verbatim}
bool Migrate(TargetGenerator& targetGen,
             Broker* broker,
             const bool forcemigration,
             const int timeout);
\end{verbatim}
\end{shaded}
will try to migrate the jobs contained in the object ({\JobController}). The jobs
will be migrated to the targets specified in {\TargetGenerator} \texttt{targetGen}
by using the broker specified by {\Broker} \texttt{broker}. The boolean
\texttt{forcemigration} specifies whether a migrated job should persist if the
new cluster ({\ExecutionTarget}) chosen by the {\TargetGenerator} does not
succeed submitting a kill/terminate request for the job. The integer
\texttt{timeout} argument have not yet been implemented.

>>>>

The \texttt{Migrate} method behaves in much the same way as the \texttt{Submit}
method, but instead of sending a new job request to the cluster it sends a 
migration request of a given job, currently this request is only supported 
for ARC1 clusters. The \texttt{url} and \texttt{jobdesc} specifies the job-id 
and {\JobDescription} of the job which should be migrated.\\
The migration request will create a new job where the local input files are 
transferred from old cluster. Once the input files have been transferred the 
new cluster will send a request to kill the old job. If the kill request is 
unsuccessful the new job will be terminated unless the \texttt{forcemigration} 
boolean is \texttt{true}.\\
The \texttt{Migrate} method will also fill the \texttt{info} {\XMLNode} with 
information about the job the same way as the \texttt{Submit} method. However 
for the \texttt{Migrate} method this \texttt{XMLNode} also contain the job-id 
of the migrated job.

@@

The \texttt{Migrate} method:
\begin{shaded}
\begin{verbatim}
bool Migrate(TargetGenerator& targetGen,
             Broker* broker,
             const bool forcemigration,
             const int timeout);
\end{verbatim}
\end{shaded}
will try to migrate the jobs contained in the object ({\JobController}). The jobs
will be migrated to the targets specified in {\TargetGenerator} \texttt{targetGen}
by using the broker specified by {\Broker} \texttt{broker}. The boolean
\texttt{forcemigration} specifies whether a migrated job should persist if the
new cluster ({\ExecutionTarget}) chosen by the {\TargetGenerator} does not
succeed sending a kill/terminate request for the job. The integer
\texttt{timeout} argument has not yet been implemented.
